### 2020-05-18 README.Rmd
add an extra example to the readme

```{r draw-gam-figure, dev = "png", fig.height = 6, fig.width = 9, dpi = 120, echo = FALSE, fig.show = "hide", message = FALSE}
set.seed(42)
df <- gamSim(eg = 1, n = 400, verbose = FALSE)
m <- gam(y ~ s(x0) + s(x1) + s(x2) + s(x3), data = df, model = "REML")
draw(m)
```

@@

@@

>>>>

```{r draw-gam-figure, dev = "png", fig.height = 6, fig.width = 9, dpi = 120, echo = FALSE, fig.show = "hide", message = FALSE}
df1 <- data_sim("eg1", n = 400, seed = 42)
m <- gam(y ~ s(x0) + s(x1) + s(x2) + s(x3), data = df1, method = "REML")
draw(m, partial_residuals = TRUE)
```

```{r draw-gam-figure-2d, dev = "png", fig.height = 6, fig.width = 9, dpi = 120, echo = FALSE, fig.show = "hide", message = FALSE}
df2 <- data_sim("eg2", n = 1000, seed = 42)
m2 <- gam(y ~ s(x, z),  data = df2, method = "REML")
draw(m2)
```

@@

    For example, the classic four term additive example from Gu & Wabha:

@@

    Or for a bivariate smooth:

    ![Estimated smooths from a GAM](man/figures/README-draw-gam-figure-2d-1.png)
